This User Guide was designed to provide first time users of Text\+Mesh Pro with a basic overview of the features and functionality of the tool.

The Text\+Mesh Pro U\+PM package is already included with the Unity Editor and as such does not require installation. Text\+Mesh Pro \char`\"{}\+T\+M\+P\char`\"{} does however require adding resources to your project which are essential for using Text\+Mesh Pro.

To import the \char`\"{}$\ast$\+T\+M\+P Essential Resources$\ast$\char`\"{}, please use the \char`\"{}$\ast$\+Window -\/$>$ Text\+Mesh\+Pro -\/$>$ Import T\+M\+P Essential Resources$\ast$\char`\"{} menu option. These resources will be added at the root of your project in the \char`\"{}$\ast$\+Text\+Mesh Pro$\ast$\char`\"{} folder.

The Text\+Mesh Pro package also includes additional resources and examples that will make discovering and learning about Text\+Mesh Pro\textquotesingle{}s powerful features easier. It is strongly recommended that first time users import these additional resources.

To import the \char`\"{}$\ast$\+T\+M\+P Examples \& Extras$\ast$\char`\"{}, please use the \char`\"{}$\ast$\+Window -\/$>$ Text\+Mesh\+Pro -\/$>$ Import T\+M\+P Examples \& Extras$\ast$\char`\"{} menu option. These resources will also be added in the same \char`\"{}$\ast$\+Text\+Mesh Pro$\ast$\char`\"{} folder inside your project.

There are two Text\+Mesh Pro components available. The first T\+MP text component is of type $<$Text\+Mesh\+Pro$>$ and designed to work with the Mesh\+Renderer. This component is an ideal replacement for the legacy Text\+Mesh component.

To add a new $<$Text\+Mesh\+Pro$>$ text object, go to\+: “$\ast$\+Game\+Object-\/$>$3D Object-\/$>$Text\+Mesh\+Pro Text$\ast$”.

The second T\+MP text component is of type $<$Text\+Mesh\+Pro\+U\+G\+UI$>$ and designed to work with the Canvas\+Renderer and Canvas system. This component is an ideal replacement for the U\+I.\+Text component.

To add a new $<$Text\+Mesh\+Pro\+U\+G\+UI$>$ text object, go to\+: “$\ast$\+Game\+Object-\/$>$U\+I-\/$>$Text\+Mesh\+Pro Text$\ast$”.

You may also wish to watch this \href{https://youtu.be/olnxlo-Wri4}{\texttt{ Getting Started}} short video which covers this topic.

We strongly recommend that you also watch the \href{https://youtu.be/qzJNIGCFFtY}{\texttt{ Font Asset Creation}} video as well as the \href{https://youtu.be/d2MARbDNeaA}{\texttt{ Working with Material Presets}} as these two topics is also key to working and getting the most out of Text\+Mesh Pro.

As mentionned in the Installation section of this guide, it is recommended that you import the \char`\"{}$\ast$\+T\+M\+P Examples \& Extras$\ast$\char`\"{} and take the time to explore each of the examples as they provide a great overview of the functionality of the tool and the many text layout and \href{http://digitalnativestudios.com/textmeshpro/docs/rich-text/}{\texttt{ rich text tags}} available in Text\+Mesh Pro.

Should you have questions or require assistance, please visit the \href{https://forum.unity.com/forums/unity-ui-textmesh-pro.60/}{\texttt{ Unity UI \& Text\+Mesh Pro}} section of the Unity forum as well as the \href{http://digitalnativestudios.com/forum/index.php}{\texttt{ Text\+Mesh Pro User Forum}} where you will find additional information, \href{http://digitalnativestudios.com/forum/index.php?board=4.0}{\texttt{ Video Tutorials}} and \href{http://digitalnativestudios.com/forum/index.php?topic=890.0}{\texttt{ F\+AQ}}. In the event you are unable to find the information you seek, always feel free to post on the \href{https://forum.unity.com/forums/unity-ui-textmesh-pro.60/}{\texttt{ Unity UI \& Text\+Mesh Pro}} section user forum.

\href{http://digitalnativestudios.com/textmeshpro/docs/}{\texttt{ Online Documentation}} is also available on Text\+Mesh Pro including Rich Text tags, Shaders, Scripting A\+PI and more. 